Measuring and optimizing machine learning interpretability

### 2019-05-24 2019-05-sommerklausur/2019-sommerklausur-molnar.Rmd
final version of slides

@@

$\Rightarrow$ Allows model comparision

@@

>>>>

## Outline

- Why measure interpretability?
- Functional Decomposition with Accumulated Local Effects
- Measures
- Application

@@

$\Rightarrow$ Allows model comparison

@@

## Summary

- Model-agnostic interpretability measures: number of features, interaction strength, main effect complexity
- Use: model comparison and optimization metric

- Implementation: \url{https://github.com/compstat-lmu/paper_2019_iml_measures}
- Paper:[https://arxiv.org/abs/1904.03867]()
